---
title: "Crowdworking"
description: |
  A study of german crowdworkers on three select platforms.
author: 
  - name: "Sandra Kawalec"
    url: https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=13&ved=2ahUKEwjxwKCI1u3eAhUS_KQKHZlACtAQFjAMegQIAhAB&url=https%3A%2F%2Fde.linkedin.com%2Fin%2Fsandra-kawalec-024a2711b&usg=AOvVaw2GrC229sMO4AU3MUoOTfV7
    affiliation: IG Metall
  - name: "Maximilian Held"
    url: https://www.maxheld.de
    affiliation: Friedrich-Alexander Universität Erlangen-Nürnberg
    affiliation_url: http://soziologie.phil.fau.de
  - name: "Verena Kasztantowicz"
    url: http://verenakasztantowicz.de/
    affiliation: Humboldt-Universität zu Berlin
    affiliation_url: https://www.erziehungswissenschaften.hu-berlin.de/de/grundschulpaed/abteilung-grundschulpaedagogik/lern-bereiche/deutsch
  - name: "Sabine Pfeiffer"
    url: https://www.sabine-pfeiffer.de
    affiliation: Friedrich-Alexander Universität Erlangen-Nürnberg
    affiliation_url: http://soziologie.phil.fau.de
date: "November 25, 2018"
output: 
  radix::radix_article:
    toc: true
    toc_depth: 2
    dev: 'svglite'
repository_url: https://github.com/soztag/crowd
creative_commons: CC BY-SA
---

```{r setup, cache = FALSE, include=FALSE}
source(file = "setup.R")
```

```{r import, include=FALSE, eval=FALSE}
source(file = "import.R")
```

```{r cleaning, include=FALSE}
source(file = "cleaning.R")
```


# Descriptives

`r nrow(crowddata)` crowdworkers participated in this study, with `r table(crowddata$study)` from the [Applause](https://www.applause.com) application testing, [Atizo](https://www.atizo.com) innovation and market research and generic [Crowdguru](https://www.crowdguru.de) crowdsourcing platforms respectively.


## Demographics

```{r, layout="l-page", fig.cap="Participants by Age, Gender and Platform", fig.width=9}
crowddata %>% 
  ggplot(mapping = aes(x = birth, fill = study)) +
  geom_histogram(binwidth = 5) +
  facet_grid(vars(gender), vars(study)) +
  scale_x_continuous(breaks = seq(1940,2000,10))  +
  theme(legend.position = "bottom")
```

Perhaps surprisingly, the crowdworkers surveyed here include young and old, with a mean age around `r 2017 - mean(crowddata$birth, na.rm = TRUE)` years. 
The typical participant is in early middle age, with a median age of `r 2017 - median(crowddata$birth, na.rm = TRUE)` years, also indicating a skew towards younger participants overall, and few older outliers.
The platform Crowdguru draws relatively more female participants, while Applause draws more male respondents.
Across all three platforms, there are roughly equal numbers of female and male respondents (`r table(crowddata$gender)`, respectively).

```{r education}
crowddata %>% 
  count(education) %>% 
  knitr::kable(caption = "Educational Attainment")
```

```{r include=FALSE}
crowddata %>% 
  filter(education == "Fachhochschulabschluss" | education == "Universitätsabschluss") %>% 
  nrow() %>% 
  divide_by(nrow(crowddata))
# percent of people
```

Participants are, overall, relatively educated, with over half reporting a tertiary degree, though this may, in part, be explained by the age structure of participants.

Only `r sum(crowddata$disability_care)` participants report caring for a sick, old or disabled person in their household, and `r sum(crowddata$children)` have children.

```{r employment}
crowddata %>% 
  count(employment) %>% 
  knitr::kable(caption = "Employment Status")
```

More than half of the participants are in some kind of regular employment, though it is unclear whether participants understood the question to include their crowdworking.

Participants report having had, on arithmetic average, `r mean(crowddata$sum_employer, na.rm = TRUE)` separate employers or periods of self-employment, though the typical respondent only reports `r median(crowddata$sum_employer, na.rm = TRUE)`, reflecting some outliers with great declared fluctuation.
In addition, responses of more than 50, or 0 employers were dropped from the analysis, because both are likely erroneous entries.

The surveyed crowdworkers assessed their professional life overall optimistically with `r table(crowddata$profession_dev)` responding "as on the rise", "unchanging" and "on the decline".


## Current Work

Study subjects said they worked, on arithmetic average, for `r mean(crowddata$sum_platforms, na.rm = TRUE)` platforms, with a range from `r min(crowddata$sum_platforms, na.rm = TRUE)` to `r max(crowddata$sum_platforms, na.rm = TRUE)`.
There were again a few erroneous entries.

```{r platforms}
crowddata %>% 
  count(platforms) %>% 
  knitr::kable(caption = "Type of Platform")
```

Testing and microjob platforms are most popular among the participants, as is also reflected in the many respondents recruited via Applause and Crowdguru.

```{r hours, layout="l-page", fig.cap="Crowdworking Hours per Month", fig.width=9}
crowddata %>% 
  filter(study != "atizo") %>% 
  select(study, h_month, h_platform) %>% 
  gather(h_month, h_platform, key = "platform", value = "hours") %>% 
  na.omit() %>% 
  ggplot(mapping = aes(x = hours, color = study, fill = study, linetype = platform)) + 
  geom_density(alpha = 0.2, trim = TRUE) +
  # facet_wrap(vars(study), ncol = 1) + 
  xlab(label = "Hours of Work per Month") +
  scale_linetype_discrete(
    breaks = c("h_month", "h_platform"),
    labels = c("All platforms", "This platform")
  ) +
  theme(legend.position = "bottom")
```

On arithmetic average, participants worked `r mean(crowddata$h_month, na.rm=TRUE)` hours per month (median `r median(crowddata$h_month, na.rm=TRUE)`), but there is a substantial amount of spread (standard deviation `r sd(crowddata$h_month, na.rm=TRUE)`).
Figure \@ref(fig:hours) displays the probability density estimates for reported hours worked on *all*, and the platform in question. ^[There are too few non-missing responses for the Atizo crowdworkers to meaningfully include in this graph.]
The figure suggests that the working hours are more broadly spread out for respondents from Crowdguru, with more participants working shorter hours for Applause.
In both cases, the amount of hours worked on the platform in question tracks quite closely the amount of hours crowdworked in total, with an arithmetic average of only `r mean(crowddata$h_month - crowddata$h_platform, na.rm = TRUE)` worked *outside* of the studied platforms.
The density estimate of the hours worked on the platform in question can sometimes be higher than the overall hours; this is because the estimate is an *aggregate* statistic.
At the individual level, all participants who reported higher hours worked on the platform in question than on all crowdworking platforms were dropped on both variables. [^dropped-both]

[^dropped-both]: Because it was impossible to figure out which of the two numbers was entered erroneously, both were dropped from the analysis for these participants.

```{r time-of-day}
crowddata %>% 
  count(time_of_day) %>% 
  knitr::kable(caption = "Predominant Working Hours")
```

There appears to be a slight preference for working in the evening, though most study subjects responded *not* working at fixed time during the day.

```{r time-of-week}
crowddata %>% 
  count(time_of_week) %>% 
  knitr::kable(caption = "Predominant Working Days")
```

Similarly, most respondends reported working throughout the week, including weekends.

```{r workspace}
crowddata %>% 
  count(workspace) %>% 
  knitr::kable(caption = "Predominant Working Locations")
```

The overwhelming majority of all participants said they worked from home.

About half of the participants (`r sum(crowddata$perm_contract)`) would like to do their current crowdworking as a permanent, regular job.


## Work and Crowdwork Expectations

The participants were surveyed on 28 items concerning expectations towards work, under two separate contexts: work in general, and crowdwork.
The items were slightly reworded to fit the two contexts.

```{r items-scores, layout="l-body-outset", fig.cap="Items, Wordings and Average Scores"}
quest %>% 
  dplyr::filter(section == "expect_work" | section == "expect_crowd") %>% 
  select(item = "var", german = "var_german", context = "section") %>% 
  spread(key = context, value = german) %>% 
  bind_cols(average_work = colMeans(crowddata$exp_work, na.rm = TRUE)) %>% 
  bind_cols(average_crowd = colMeans(crowddata$exp_crowd, na.rm = TRUE)) %>% 
  bind_cols(average_diff = colMeans(crowddata$exp_work - crowddata$exp_crowd, na.rm = TRUE)) %>% 
  DT::datatable(
    rownames = FALSE,
    options = list(
      pageLength = 5
    )
  ) %>% 
  DT::formatRound(columns = 4:6)
```

It should be noted that the items between the two batteries (work and crowdwork) are not strictly comparable.
These differences are sometimes above and beyond, or unrelated to the change context.
For example, item `fair` is worded "to be treated fairly" for the crowdwork context, and "to be treated fairly *at work*" (emphasis added) for the regular work context.
Such subtle shifts in emphasis may contribute small shifts in ratings, or may, in any event, make it hard to compare the ratings between the two contexts.


```{r battery, fig.cap=paste(c("Work", "Crowdwork"), "Expectations (Heatmap of Counts)"), layout = "l-screen", fig.width=12, fig.height=10}
plot_battery <- function(m, long) {
  # name long y labels, so they can be used as named vectors to replace existing short labels in the below
  long %>% 
    set_names(value = colnames(crowddata$exp_work)) %>% 
    stringr::str_wrap(width = 65) %>% 
    {.} -> long
  
  # munge data
  m %>% 
    as_tibble() %>% 
    add_column(study = crowddata$study) %>% 
    gather(key = "item", value = "score", -study) %>% 
    ggplot(
      mapping = aes(
        x = as.factor(score), 
        y = item, 
        fill = study,
        alpha = stat(count)
      )
    ) +
    stat_bin_2d() + 
    facet_wrap(vars(study), nrow = 1) + 
    theme(
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      legend.position = "bottom"
    ) +
    xlab("Agreement with Statement") +
    ylab(label = NULL) +
    scale_fill_discrete(name = "Platforms") + 
    guides(fill = FALSE) + 
    scale_y_discrete(labels = long)
}

quest %>%
  dplyr::filter(section == "expect_work") %>% 
  pull(var_german) %>% 
  {.} -> long
plot_battery(m = crowddata$exp_work, long = long)

quest %>%
  dplyr::filter(section == "expect_crowd") %>% 
  pull(var_german) %>% 
  {.} -> long
plot_battery(m = crowddata$exp_crowd, long = long)
```

The above figures \@ref(fig:items-scores) and \@ref(fig:battery) show relatively little variance within and across the measured 28 variables in both contexts.
Most participants rate most of the items as relatively important, or very important.
Hardly any respondents and hardly any variables include negative ratings ("does not apply at all", "does not apply").
This does not bode well for a correlation analysis or dimensionality reduction: there is just not enough variance on either the people or variable mode in the data matrix to expect much structure.


```{r difference, fig.cap="Work - Crowd Expectations (Heatmap of Counts)", layout = "l-screen", fig.width=12, fig.height=10}
plot_battery(
  m = crowddata$exp_work-crowddata$exp_crowd, 
  long = colnames(crowddata$exp_work)
)
```

There is also not much difference in the rankings of the variable compared between the two contexts.
In figure \@ref(fig:difference), the individual crowdwork scores are subtracted from the work scores, and the results are then counted.
For example, the counts for a `-3` in figure \@ref(fig:difference) is the number of participants who rate the item in question *3* levels higher in the crowd than in the regular work context.
There are, alas, very view such substantial differences. 
Most of the participants rate the statements very similarly for the two contexts.

