---
title: "Crowdworking"
description: |
  A study of german crowdworkers on three select platforms.
author: 
  - name: "Sandra Kawalec"
    url: https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=13&ved=2ahUKEwjxwKCI1u3eAhUS_KQKHZlACtAQFjAMegQIAhAB&url=https%3A%2F%2Fde.linkedin.com%2Fin%2Fsandra-kawalec-024a2711b&usg=AOvVaw2GrC229sMO4AU3MUoOTfV7
    affiliation: IG Metall
  - name: "Maximilian Held"
    url: https://www.maxheld.de
    affiliation: Friedrich-Alexander Universität Erlangen-Nürnberg
    affiliation_url: http://soziologie.phil.fau.de
  - name: "Verena Kasztantowicz"
    url: http://verenakasztantowicz.de/
    affiliation: Humboldt-Universität zu Berlin
    affiliation_url: https://www.erziehungswissenschaften.hu-berlin.de/de/grundschulpaed/abteilung-grundschulpaedagogik/lern-bereiche/deutsch
  - name: "Sabine Pfeiffer"
    url: https://www.sabine-pfeiffer.de
    affiliation: Friedrich-Alexander Universität Erlangen-Nürnberg
    affiliation_url: http://soziologie.phil.fau.de
date: "November 25, 2018"
output: 
  radix::radix_article:
    toc: true
    toc_depth: 2
    dev: 'svglite'
repository_url: https://github.com/soztag/crowd
creative_commons: CC BY-SA
---

```{r setup, cache = FALSE, include=FALSE}
source(file = "setup.R")
```

```{r import, include=FALSE, eval=FALSE}
source(file = "import.R")
```

```{r cleaning, include=FALSE}
source(file = "cleaning.R")
```


# Descriptives

`r nrow(crowddata)` crowdworkers participated in this study, with `r table(crowddata$study)` from the [Applause](https://www.applause.com) application testing, [Atizo](https://www.atizo.com) innovation and market research and generic [Crowdguru](https://www.crowdguru.de) crowdsourcing platforms respectively.

```{r, layout="l-page", fig.cap="Participants by Age, Gender and Platform", fig.width=9}
crowddata %>% 
  ggplot(mapping = aes(x = birth, fill = study)) +
  geom_histogram(binwidth = 5) +
  facet_grid(vars(gender), vars(study)) +
  scale_x_continuous(breaks = seq(1940,2000,10))
```

Perhaps surprisingly, the crowdworkers surveyed here include young and old, with a mean age around `r 2017 - mean(crowddata$birth, na.rm = TRUE)` years. 
The typical participant is in early middle age, with a median age of `r 2017 - median(crowddata$birth, na.rm = TRUE)` years, also indicating a skew towards younger participants overall, and few older outliers.
The platform Crowdguru draws relatively more female participants, while Applause draws more male respondents.
Across all three platforms, there are roughly equal numbers of female and male respondents (`r table(crowddata$gender)`, respectively).



